Exploring the Validity Range of PLL Analytical Models

### 2025-05-29 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Empirically adjusted loop parameters (phase error limit and loop DC gain) to match simulation with theory.

theta_e_m_n = math.sin(omega_n*math.sqrt(1-zeta**2)*t_m)/(math.sqrt(1-zeta**2))*math.e**(-zeta*omega_n*t_m)
theta_e_m = math.pi
```

@@

# Parâmetros iniciais
f_r = 10e6
f_o = 50e6
N = 5
Kvco = KVCO = 10e6
I = 1e-3
K_theta = Kphase = I / (2 * np.pi)
A0 = 6
K = A0 * Kphase * KVCO / N
```

>>>>

theta_e_m_n = math.sin(omega_n*math.sqrt(1-zeta**2)*t_m)/(math.sqrt(1-zeta**2))*math.e**(-zeta*omega_n*t_m)
theta_e_m = (1.6255) * math.pi
```

@@

# Parâmetros iniciais
f_r = 10e6
f_o = 50e6
N = 5
Kvco = KVCO = 10e6
I = 1e-3
K_theta = Kphase = I / (2 * np.pi)
A0 = 6.258
K = A0 * Kphase * KVCO / N
```
